Home

### 2017-09-29 analysis/applyflahr2onsimulations.Rmd
Files commited by wflow_commit.

```{r}
library(cowplot)
set.seed(99)
L_se = c( 0.25, 0.5, 1, 2, 4)
L_pi = c(1, 1,1,1,1)
L_pi = L_pi / sum(L_pi)
N = 200
P = 300
Data = datamaker(N,P,L_pi,L_se,0.1,c(1),c(1),1,sqrt(1))
#Data = datamaker(N,P,L_pi,L_se,0.36,c(1),c(1),1,sqrt(1))
dim(Data$Y)
# = flashr::flash(Data$Y)
data = flashr2::flash_set_data(Data$Y)
gf = flashr2::flash_r1(data,verbose=FALSE)

@@

g2 <- ggplotGrob(zoomed2)
base2 +annotation_custom(grob = g2, xmin = -0.6, xmax = -0.1, ymin = -0.05, ymax = 0.45)
plot_grid(base1, base2, zoomed1,zoomed2, labels = "AUTO", ncol = 2)

@@

```{r}
library(cowplot)
set.seed(99)
L_se = c( 0.25, 0.5, 1, 2, 4)
L_pi = c(1, 1,1,1,1)
L_pi = L_pi / sum(L_pi)
N = 200
P = 300
Data = datamaker(N,P,L_pi,L_se,0.7,c(1),c(1),1,sqrt(16))
dim(Data$Y)
data = flashr2::flash_set_data(Data$Y)
gf = flashr2::flash_r1(data,verbose=FALSE)
PMDlog = capture.output({gPMD = invisible( PMA.wrapper(Data$Y)) })

@@

```{r}
set.seed(99)
N = 150
P = 240
K = 3
L_true = array(0,dim = c(N,K))
F_true = array(0,dim = c(P,K))
F_true[1:80,1] = rnorm(80,0,0.5)
F_true[81:160,2] = rnorm(80,0,1)
F_true[161:240,3] = rnorm(80,0,2)
L_true[1:10,1] = rnorm(10,0,2)
L_true[11:60,2] = rnorm(50,0,1)
L_true[61:150,3] = rnorm(90,0,0.5)
G = L_true %*% t(F_true)
# generate Y
E = matrix(rnorm(N*P,0,2),nrow=N)
Y = L_true %*% t(F_true) + E

>>>>

```{r,message=FALSE,warning=FALSE}
library(cowplot)
set.seed(99)
L_se = c( 0.25, 0.5, 1, 2, 4)
L_pi = c(1, 1,1,1,1)
L_pi = L_pi / sum(L_pi)
N = 200
P = 300
Data = datamaker(N,P,L_pi,L_se,0.1,c(1),c(1),1,sqrt(1))
#Data = datamaker(N,P,L_pi,L_se,0.36,c(1),c(1),1,sqrt(1))
dim(Data$Y)
# = flashr::flash(Data$Y)
data = flashr2::flash_set_data(Data$Y)
gf = flashr2::flash_r1(data,verbose=FALSE)

@@

g2 <- ggplotGrob(zoomed2)
base2 +annotation_custom(grob = g2, xmin = -0.6, xmax = -0.1, ymin = -0.05, ymax = 0.45)
# plot_grid(base1, base2, zoomed1,zoomed2, labels = "AUTO", ncol = 2)

@@

```{r,message=FALSE,warning=FALSE}
library(cowplot)
set.seed(99)
L_se = c( 0.25, 0.5, 1, 2, 4)
L_pi = c(1, 1,1,1,1)
L_pi = L_pi / sum(L_pi)
N = 200
P = 300
Data = datamaker(N,P,L_pi,L_se,0.7,c(1),c(1),1,sqrt(16))
dim(Data$Y)
data = flashr2::flash_set_data(Data$Y)
gf = flashr2::flash_r1(data,verbose=FALSE)
PMDlog = capture.output({gPMD = invisible( PMA.wrapper(Data$Y)) })

@@

```{r,message=FALSE,warning=FALSE}
set.seed(99)
N = 150
P = 240
K = 3
L_true = array(0,dim = c(N,K))
F_true = array(0,dim = c(P,K))
F_true[1:80,1] = rnorm(80,0,0.5)
F_true[81:160,2] = rnorm(80,0,1)
F_true[161:240,3] = rnorm(80,0,2)
L_true[1:10,1] = rnorm(10,0,2)
L_true[11:60,2] = rnorm(50,0,1)
L_true[61:150,3] = rnorm(90,0,0.5)
G = L_true %*% t(F_true)
# generate Y
E = matrix(rnorm(N*P,0,2),nrow=N)
Y = L_true %*% t(F_true) + E

### 2017-09-29 analysis/index.Rmd
Files commited by wflow_commit.

Click here to find [null check for flashr2](NULLcheck.html)

>>>>

Click here to find the [null check for flashr2](NULLcheck.html) and [densen nu case](nullcheck2.html)

### apply flashr2 for the examples in FLASH paper

#### simulations

Click here to check the [simulatoin result (rank one and rank three)](applyflahr2onsimulations.html)
